---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}
@import url('https://fonts.googleapis.com/css2?family=Balsamiq+Sans:ital,wght@0,400;0,700;1,400;1,700&display=swap');

html {
  display: flex;
  justify-content: center;
}

body {
  font-family: "Balsamiq Sans", sans-serif;
  background-color: #f5f0e7; /* cream color */
  font-size: 24px;
  display: inline-block;
}

h3 {
  color: teal;
}

h2 {
  color: orange;
}

div.section.level2 {
  border: 2px dashed oklch(0.648 0.2 131.684);
  margin-bottom: 20px;
  padding-left: 10px;
  padding-right: 10px;
}
div.section.level3 {
  border: 2px dashed blue;
  margin-bottom: 20px;
  padding-left: 10px;
  padding-right: 10px;
  display: inline-block;
}
```

## Sleep Duration and Quality Tracker

This website dynamically creates a bar chart and summaries for the data collected from a Google form sheet!

```{r}
library(tidyverse)

logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vRKI8naOEo40slXbBPQhcZ7Iq4daGwm8NXxqzj61ItZ0-eIDDbbBVgS5qunhTLr0_w_m2GOs4yWTSUV/pub?output=csv")


latest_data <- logged_data %>% rename(date_of_sleep = 2, 
                                      sleep_duration = 3, 
                                      sleep_quality = 4)

sleep_duration_bar_chart <- latest_data %>%
                            ggplot() +
                            geom_bar(aes(x = sleep_duration, fill=sleep_quality)) +
                            theme(plot.background = element_rect(fill="#f5f0e7"))

sleep_quality_bar_chart <- latest_data %>%
                           ggplot() +
                           geom_bar(aes(x = sleep_quality)) +
                           theme(plot.background = element_rect(fill="#f5f0e7"))
            

mean_sleep_duration <- latest_data$sleep_duration %>% mean()
highest_sleep_duration <- latest_data$sleep_duration %>% max()
lowest_sleep_duration <- latest_data$sleep_duration %>% min()

bad_count <- length(latest_data$sleep_quality[latest_data$sleep_quality == "Bad"])
fair_count <- length(latest_data$sleep_quality[latest_data$sleep_quality == "Fair"])
good_count <- length(latest_data$sleep_quality[latest_data$sleep_quality == "Good"])
total_sleep_count <- length(latest_data$sleep_quality)
```

## Sleep Duration Data Chart

```{r}
sleep_duration_bar_chart
```

### Sleep Duration Metrics
Mean Sleep Duration: `r mean_sleep_duration`

Longest Sleep Duration: `r highest_sleep_duration`

Shortest Sleep Duration: `r lowest_sleep_duration`

## Sleep Quality Data Chart

```{r}
sleep_quality_bar_chart
```

### Sleep Quality Metrics

Bad Sleep Count: `r bad_count` / `r total_sleep_count`

Fair Sleep Count: `r fair_count` / `r total_sleep_count`

Good Sleep Count: `r good_count` / `r total_sleep_count`


## Sleep Duration and Sleep Quality Correlation

```{r}
summary_data <- latest_data %>%
  group_by(sleep_quality) %>%
  summarize(
    mean = mean(sleep_duration, na.rm = TRUE), # get the mean(displayed as a point)
    lower_quartile = quantile(sleep_duration, 0.25, na.rm = TRUE), # get the bottom 25% of the data
    upper_quartile = quantile(sleep_duration, 0.75, na.rm = TRUE) # get the top 25% of the data
  )


ggplot(summary_data, aes(x = mean, y = sleep_quality)) +
  geom_point(color = "blue", size = 3) +  # mean points
  geom_errorbarh(aes(xmin = lower_quartile, xmax = upper_quartile), height = 0.2, color = "red") +  # error bars with quantile
  labs(
    title = "Sleep Duration Summary by Sleep Quality",
    x = "Sleep Duration (hours)",
    y = "Sleep Quality"
  ) +
  theme_minimal()
```

Trend: Higher duration of sleep tend to result in a higher quality of sleep.
